Leaf traits and size drive differences in above-ground biomass distribution among woody plant functional types

### 2016-02-01 manuscript.Rnw
Moved back to remake

print(xtable(table_hierpart),sanitize.text.function=function(x){x},
      include.rownames=FALSE)

@@

<<results='asis'>>=
library(stargazer)
m0 <- lme(lmlf_mst ~ lh.t, random=~1|Group, data=dataset, na.action=na.omit)
m1 <- lme(lmlf_mst ~ lh.t*pft, random=~1|Group, data=dataset, na.action=na.omit)

stargazer(m0,m1)
@

>>>>

print(xtable(table_varpart_gam),sanitize.text.function=function(x){x},
      include.rownames=FALSE)

@@
